Dynein walks like an Imperial AT-ST

### 2018-08-10 papers/paper/paper.tex
Add new plots to paper. TODO: make them look nicer

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_dwell_time_histogram}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:}
\end{figure}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_histogram.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}

>>>>

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}%
  \includegraphics[width=0.5\linewidth]{../../plots/paper_dwell_time_histogram}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}%
  \includegraphics[width=0.5\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:}
\end{figure}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}%
  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_histogram.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}
